Cloud Supercomputing

### 2019-04-15 writing/paper/paper.tex
Fix bibliography style, add acknowledgements.

\documentclass[runningheads]{llncs}
\title{Cloud Supercomputing}
\author{Lukas Krenz\inst{1} \and{} Leonhard Rannabauer\inst{1} \and{} Michael Bader\inst{1}}
\institute{Technical University of Munich}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage[american]{babel}
\usepackage[autostyle, english = american]{csquotes}
\usepackage[%
  % backend=biber,
  % url=false,
  % style=alphabetic,
  % backref=true,
  % hyperref=true,
  % maxnames=4,
  % minnames=3,
  % maxbibnames=99,
  % firstinits,
  % uniquename=init
  ]{biblatex}
\DefineBibliographyStrings{english}{%
  backrefpage = {see p.},
  backrefpages = {see pp.}
}
\addbibresource{../bibliography.bib}

@@

>>>>

\documentclass[runningheads]{llncs}
\title{Cloud Supercomputing}
\author{Lukas Krenz\inst{1} \and{} Leonhard Rannabauer\inst{1} \and{} Michael Bader\inst{1}}
\institute{Technical University of Munich} % todo emails and stuff
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage[american]{babel}
\usepackage[autostyle, english = american]{csquotes}
\usepackage[%
  backend=biber,
  url=false,
  doi=false,
  % style=alphabetic,
  % backref=true,
  % hyperref=true,
  maxnames=3,
  % minnames=3,
  % maxbibnames=99,
  firstinits=true,
  % uniquename=init
  ]{biblatex}
\DefineBibliographyStrings{english}{%
  backrefpage = {see p.},
  backrefpages = {see pp.}
}
\addbibresource{../bibliography.bib}

@@

\subsection*{Acknowledgements}
Lukas Krenz was funded by ChEESE (823844), Leonhard Rannabauer was funded by ExaHyPE (671698).
\todo{LK: Standard sentence is: This research was funded by the European Union’s Horizon 2020 Research and Innovation Programme under theproject ExaHyPE, grant no.  671698 (call FETHPC-1-2014).

Also LRZ?}
